Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2025-01-12 paper/main.tex
minor updates to paragraph introducing fig 8 results

Knowledge estimates need not be limited to the content of the lectures. As
illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
estimating knowledge from a small number of quiz questions may be extended to
\textit{any} content, given its text embedding coordinate. To visualize how
knowledge ``spreads'' through text embedding space to content beyond the
lectures participants watched, we first fit a new topic model to the lectures'
sliding windows with $k = 100$~topics. Conceptually, increasing the
number of topics used by the model functions to increase the ``resolution'' of
the embedding space, providing a greater ability to estimate knowledge for
content that is highly similar to (but not precisely the same as) that
contained in the two lectures. We note that we used these 2D maps solely for
visualization; all relevant comparisons, distance computations, and statistical
tests we report above were carried out in the original 15-dimensional space,
using the 15-topic model. Aside from increasing the number of topics from 15 to
100, all other procedures and model parameters were carried over from the
preceding analyses. As in our other analyses, we resampled each lecture's topic
trajectory to 1~Hz and projected each question into a shared text embedding
space.

>>>>

Knowledge estimates need not be limited to the contents of these particular
lectures and quizzes. As illustrated in Figure~\ref{fig:knowledge-maps}, our 
general approach to estimating knowledge from a small number of quiz questions 
may be extended to \textit{any} content, given its text embedding coordinate. To 
visualize how knowledge ``spreads'' through text embedding space to content 
beyond the lectures participants watched and the questions they answered, we 
first fit a new topic model to the lectures' sliding windows with $k = 
100$~topics. Conceptually, increasing the number of topics used by the model 
functions to increase the ``resolution'' of the embedding space, providing a 
greater ability to estimate knowledge for content that is highly similar to (but 
not precisely the same as) that contained in the two lectures used to train the 
model. We note that we used these 2D maps solely for visualization; all relevant 
comparisons, distance computations, and statistical tests we report above were 
carried out in the original 15-dimensional space, using the 15-topic model. 
Aside from increasing the number of topics from 15 to 100, all other procedures 
and model parameters were carried over from the preceding analyses. As in our 
other analyses, we resampled each lecture's topic trajectory to 1~Hz and 
projected each question into a shared text embedding space.
